\Huge \bf \sc Calibration of an inertial measurement unit

### 2013-07-29 latex/paper_sensores/paper.tex
más paper

\begin{itemize}
\item The typical sensitivity for each axis is $256 bits/g \approx 26.10 m^{s-2}$.
\item The typical offset for each axis is $0 ms^{-2}$.
\item As the axis should be as orthogonal as possible is reasonable to think that the rotation angles $\alpha_{aij}$ are near zero. 
\end{itemize}

@@

\begin{equation}
\mu = -0.03ms^{-2}, \; \sigma = 0.06ms^{-2}
\end{equation}

@@

On the other hand, the typical offset error is $\pm 40 ^\circ s^{-1}$
\subsection{Temperature adjust}

>>>>

\begin{itemize}
\item The typical sensitivity for each axis is $256 bits/g \approx 26.10 bits / m^{s-2}$.
\item The typical offset for each axis is $0 ms^{-2}$.
\item As the axis should be as orthogonal as possible is reasonable to think that the rotation angles $\alpha_{aij}$ are near zero. 
\end{itemize}

@@

\begin{equation}
\mu_a = -0.03ms^{-2}, \; \sigma_a = 0.06ms^{-2}
\end{equation}

@@

On the other hand, the typical offset error is $\pm 40 ^\circ s^{-1}$, this correspond to an error of $\pm 574 bits$. All the offsets estimated are smaller than this value, representing in the worst case only the $5.8 \%$ than the maximum declared in the datasheets. \\

Last but not least, the results over the test set are the following:

\begin{equation}
\mu_\omega = 6.67 \times 10^{-3} rad/s\, \sigma_\omega = 7.4 \times 10^{-3} rad/s
\end{equation}

The mean and the standard deviation obtained both correspond to aproximatelly $6$ bits errors.

As we can see the error obtained, in terms of bits, is bigger for the gyroscope than for the accelerometer. The main reason for this to happen is that in this case we are working with a scale that is not optimal, yet the only one available, for the speed of interest. The maximal angular speed measured ($198 ^{\circ} /s$ ) is approximately a tenth of the scale of the gyroscope ($2000^{\circ} /s$) while for the accelermoeter the maximal acceleration measured ($g$) is the half of the scale used ($2 g$).

\subsection{Temperature adjust}
